\markboth{Acknowledgements}{}

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

This graduation project consumed huge amount of work, research and dedication. Still, accomplishment would not have been possible if we did not have a support of many individuals. Therefore we would like to extend our sincere gratitude to all of them.

%advisor
First of all, we would like to sincerely thank our advisors Dr.Ing. Mohammed Nour. For giving us the opportunity to work on great ideas with great people . When needing someone for the
discussion of any problem, he was always there and also solved a lot of problems for/with us.


we are also grateful to our friend and Teaching Assistant, Mahmoud Ibrahim. For helping us a lot with providing the martial for the robot.


We would like to thank all the numerous people in the Internet who ask questions and provide answers for programming problems (specifically in ROS) and for the very useful code and tools they share with others.

%family and friends
we would like to most importantly acknowledge the effort of our families, who encouraged us to pursue higher education and support us through the difficulties associated with such a goal even when we was not sure we would make it through. 

Last but not least, we would like to thank our friends for always encouraging us onwards. We can
never thank them enough for their love and faith.

%Egypt
This work was supported by a financial aid  from Zagazig University. We would like to thank the funders. They had no role in study design, data collection and analysis, decision to publish, or preparation of this work.
