\markboth{Abstract}{}
\addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract}
This report is a documentation of the final year graduation project in electrical engineering at zagazig university. The purpose of this project is to Design, Construction and Control of a six-legged walking robot that is capable of basic mobility tasks such as walking forward, backward, rotating in place and raising or lowering the body height.

The legs are of a modular design that have three degrees of freedom each. This robot will serve as a platform onto which additional sensory components could be added, or which could be programmed to perform increasingly complex tasks.

The components that make up our final design are discussed. Also, we describe the basic robot gaits of locomotion for efficient navigation. This locomotion is tuned to make the robot faster and at same time energy efficient to navigate and negotiate difficult terrain.

The robot is an integrated multi-legged walking robot based on de-facto standard Robotic Operating System (ROS) that employs novel and different walking patterns.

Our robot is teleoperated using hand-held devices such as a smart phone or tablet or a wireless joystick. Furthermore, it has its own navigation system and a camera for instant video recording and streaming.

The power to the entire system is supplied through two 5 volts NiMH batteries. There is an additional power bank to power up the Raspberry Pi and other electronic components. 
We have an interactive website for robot inspection and online control in addition to leaning materials such as robot building and implementation walkthroughs and as well as step-by-setup tutorials.\\


\textbf{Keywords} -- biologically inspired, legged robot, gait generation, design procedure, simulation

